---
title: "Lab 00 - Hello IDS!"
author: "freddoderfisch"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Peter Rabbit", "Freddo Elson", "Aimee Tumblety", 
           "Felix Ainsley", "Katya Cheltsova", "Kayleigh Innes"),
  github_username = c("mcgregor-garden", "freddoderfisch", "aimeet05", 
                      "fjainsley", "katya-c", "Kayleighinnes"), 
  colour = c("powderblue", "orange", "blue", 
             "purple", "blue", "green"),
  hobby = c("Hopping", "gym", "guitar", 
            "tabletennis", "piano", "watching films"),
  favourite_number = c(2, 4, 7, 13, 4, 69)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


It shows our favourite numbers ranked and the bars are our favourite colours

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "usernames", 
          y = "favourite number",
          title = "The Teams Favourite Numbers")
```

It allows you to give your graph axis titles and a heading

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

It is bad cos everyone got different hobbies so if it was extrapolated t the whole class there would just be a lot of bar charts with the same value. A table would be a better representation of the data.
